### 2019-09-22 proglog.tex
add plasma panels

\subsubsection{Critical Conversations: Microreactors}
This panel explores the benefits of microreactors in general. It will also explore the idea of universities as potential markets for microreactors. Microreactors are exactly what they sound like,

\subsubsection{Applications for Plasma Processing}

\subsubsection{Fusion: Materials for the Future}

\subsubsection{Nuclear Policy and Legislation}
Nuclear energy is one of the most heavily regulated fields in the United States. This panel aims to enlighten attendees about how legislation is written and how non-scientist government officials might better understand the potential of nuclear energy. This panel will allow attendees to learn who is working in this area and develop a network of people devoted to issues of nuclear policy.
Rita Baranwal would be an excellent speaker on this panel because of her work for the DOE.\\

>>>>

\subsubsection{Critical Conversations: Microreactors}
Microreactors are a growing area of nuclear research and the first installations have been projected for some time in the mid 2020s. They are capable of generating 1-50 MWth, which can be used directly or converted to electricity. These relatively portable reactors are capable of powering remote areas and towns with little infrastructure. UIUC has stated that it aims to be carbon neutral by 2050. The University is exploring the possibility of constructing a microreactor on campus for research and power generation, a first of its kind, in pursuit of its decarbonization goals. This panel will discuss the benefits and applications for microreactors around the world and also talk specifically about the potential market for microreactors on universities. We have a several groups on campus researching, simulating, and modelling microreactors. Faculty leading these groups would be excellent speakers on this panel.

\subsubsection{Applications for Plasma Processing}
Plasma processing has become a staple in many fields of advanced manufacturing. Without plasma, modern conveniences such as smartphones and powerful computer technology would not be possible. In this panel, representatives from companies at the cutting-edge of plasma processing research will discuss how plasmas continue to revolutionize contemporary industry. Potential panelists include Brian Jurczyk, CEO of Starfire Industries, and Phi Nguyen, former Vice President and Director of Engineering at Intel Corp.

\subsubsection{Fusion: Materials for the Future}
Nuclear fusion has the potential to serve as the ultimate clean energy source, capable of supplying the world’s energy needs for millennia. Harnessing this immensely powerful energy resource requires further innovation in a variety of scientific disciplines. One of the largest remaining obstacles to fusion energy is the unprecedented strain placed on the materials from which fusion reactors are built. This panel will focus on the latest advancements in plasma facing components research and could feature panelists such as Professor David Ruzic, director of the UIUC Center for Plasma-Material Interactions, and Dr. Lauren Garrison, Weinberg Fellow at ORNL.

\subsubsection{Nuclear Policy and Legislation}
Nuclear energy is one of the most heavily regulated fields in the United States. This panel aims to enlighten attendees about how legislation is written and how non-scientist government officials might better understand the potential of nuclear energy. This panel will allow attendees to learn who is working in this area and develop a network of people devoted to issues of nuclear policy.
Rita Baranwal would be an excellent speaker on this panel because of her work for the DOE.

\subsubsection{Radiological Techonology for a Healthier and Safer Future}
From the production of medical isotopes to nuclear verification, radiological engineering will play an important role in the future of health, security, and more. This panel will illuminate some of those applications and show attendees what could be possible with radiological technology. Speakers may include Greg Piefer from SHINE and Ross Radel from Phoenix.\\
